---
title: "Project"
author: "Crystal Fan, Kristy Yu"
date: "2023-02-25"
output: html_document
---
```{r}
library(dplyr)
library(ggplot2)

```

```{r}
Project <- read.csv("~/Documents/marketing580/project.csv")

head(Project)
```

#H1: (with or without) VS conversion rate at store level
```{r}
chisq.test(Project$Label, Project$Purchased_Or_Not, correct=FALSE)
```


#H2: (with or without) VS conversion rate at dish level
```{r}
chisq.test(Project$Label, Project$Purchased_2, correct=FALSE)
```

#H3-1: (with_55 or without) VS conversion rate at dish level
```{r}
chisq.test(Project$Label1, Project$Purchased_2, correct=FALSE)
```

#H3-2: (with_70 or without) VS conversion rate at dish level
```{r}
chisq.test(Project$Label2, Project$Purchased_2, correct=FALSE)
```

#H3-3: (with_85 or without) VS conversion rate at dish level
```{r}
chisq.test(Project$Label3, Project$Purchased_2, correct=FALSE)
```

#H3-1: (with_55 or with_70) 
```{r}
H3_data1 = Project %>% filter(Label1 == 1|Label2 == 1)

chisq.test(H3_data1$Label1, H3_data1$Purchased_2, correct=FALSE)
```

#H3-2: (with_55 or with_85) 
```{r}
H3_data2 = Project %>% filter(Label1 == 1|Label3 == 1)

chisq.test(H3_data2$Label1, H3_data2$Purchased_2, correct=FALSE)
```

#H3-3: (with_70 or with_85) 
```{r}
H3_data3 = Project %>% filter(Label2 == 1|Label3 == 1)

chisq.test(H3_data3$Label2, H3_data3$Purchased_2, correct=FALSE)
```

#H4: (with or without) VS conversion rate at dish level by income level
```{r}
H4 = glm(Purchased_2~Label*Income, data = Project)
summary(H4)
```


#H5: (with or without) VS conversion rate at dish level by education level
```{r}
H5 = glm(Purchased_2~Label*Education, data = Project)
summary(H5)
```



#H6: (with or without) VS conversion rate at dish level by frequency
```{r}
H6 = glm(Purchased_2~Label*ba1_1Frequency, data = Project)
summary(H6)
```


#H7: (with or without) VS conversion rate at dish level by ethinical 
```{r}
H7 = glm(Purchased_2~Label*Ethnicity, data = Project)
summary(H7)
```


#H8: (with or without) VS conversion rate at dish level by gender 
```{r}
H8 = glm(Purchased_2~Label*Gender, data = Project)
summary(H8)
```


#H9: (with or without) VS conversion rate at dish level by age 
```{r}
H9 = glm(Purchased_2~Label*age_1, data = Project)
summary(H9)
```


#H10: (with or without) VS conversion rate at dish level by marital 
```{r}
H10 = glm(Purchased_2~Label*marital, data = Project)
summary(H10)
```


#H11(with or without) VS conversion rate at dish level by marital
```{r}
H11 = glm(Purchased_2~Label*sex_or, data = Project)
summary(H11)
```